ZCB Pricing

### 2018-08-06 Draft.tex
dsfs

$$B_{i-1,j}=pu_{j}B_{i,j-1}+pm_{j}B_{i,j}+pd_{j}B_{i,j+1}$$

@@

Note that:       
$$pu_{j}=(r_j/\Delta t)^{-1}(\frac{\sigma^{2}}{2(\Delta r_j)^{2}}+\frac{\alpha-\beta r_j}{2\Delta r_j})$$
$$pm_{j}=(r_j/\Delta t)^{-1}(\frac{1}{\Delta t}-\frac{\sigma^2}{\Delta r_j}^{2})$$
$$pd_{j}=(r_j/\Delta t)^{-1}(\frac{\sigma^{2}}{2(\Delta r_j)^{2}}+\frac{\alpha-\beta r_j}{2\Delta r_j})$$

@@

$$\begin{bmatrix}
	B_{i-1,1} \\
	B_{i-1,2} \\
	\vdots \\       
	B_{i-1,n-1}
	\end{bmatrix}
=
\left( \begin{array}{cccccc}
pm_{1} & pd_{1} & 0 & \cdots  & 0 & 0\\
pu_{2} & pm_{2} & pd_{2} &\cdots & 0 & 0 \\
& pu_{3} & pm_{3} & \cdots & 0 & 0  \\
& \vdots &\vdots & \ddots & \vdots & \vdots \\ 
& 0 & 0 & \cdots & pu_{n-1} & pm_{n-1} \end{array} \right) 
%
\begin{bmatrix}
	B_{i,1} \\
	B_{i,2} \\
	\vdots \\       
	B_{i,n-1}
\end{bmatrix}
+
 \begin{bmatrix}
	pu_{1}B_{i,0} \\
	0 \\
	\vdots \\
	0 \\
	pd_{j-1}B_{i,n-1}
	\end{bmatrix}  
$$

@@

$$B_{i+1,j}= pu_{j}B_{i,j-1}+pm_{j}B_{i,j}+pd_{j}B{i,j+1} $$

@@

$$pu_{j}= (\frac{\alpha-\beta r_{j+1}}{2\Delta r} - \frac{\sigma^2}{2\Delta r^2})\Delta t$$ 
$$pm_{j}= (r_{j+1}+\frac{1}{\Delta t} + \frac{\sigma^2}{\Delta r ^2})\Delta t$$
$$pd_{j}= (\frac{\alpha-\beta r_{j+1}}{2\Delta r} + \frac{\sigma^2}{2\Delta r^2})(-\Delta t) $$

@@

$$\left( \begin{array}{cccccc}
pm_{1} & pd_{1} & 0 & \cdots  & 0 & 0\\
pu_{2} & pm_{2} & pd_{2} &\cdots & 0 & 0 \\
& pu_{3} & pm_{3} & \cdots & 0 & 0  \\
& \vdots &\vdots & \ddots & \vdots & \vdots \\ 
& 0 & 0 & \cdots & pd_{n-1} & pm_{n-1} \end{array} \right)
%
\begin{bmatrix}
B_{i,1} \\
B_{i,2} \\
\vdots \\
B_{i,n-1}
\end{bmatrix}
=
\begin{bmatrix}
B_{i+1,1} \\
B_{i+1,2} \\
\vdots \\
B_{i+1,r_{n-1}}
\end{bmatrix}
+
\begin{bmatrix}
-pu_{1}B_{i,0} \\
0 \\
\vdots \\
0 \\
-pd_{j-1}B_{i, r_{n-1}}
\end{bmatrix}
$$

@@

$$pu_{j}=\frac{\alpha-\beta r_{j+1}}{4\Delta r} - \frac{\sigma^2}{4\Delta r^2}$$
$$pm_{j}= \frac{\sigma^2}{2 (\Delta r)^2}+\frac{r_{j}}{2}$$
$$pd_{j}=-\frac{\alpha-\beta r_{j+1}}{4\Delta r} - \frac{\sigma^2}{4\Delta r^2}$$

@@

$$ \left( \begin{array}{cccccc}
-(1/\Delta t)-pm_{1} & -pd_{1} & 0 & \cdots  & 0 & 0\\
-pu_{2} & -(1/\Delta t)-pm_{2} & -pd_{2} &\cdots & 0 & 0 \\
& -pu_{3} & -(1/\Delta t)-pm_{3} & \cdots & 0 & 0  \\
& \vdots &\vdots & \ddots & \vdots & \vdots \\ 
& 0 & 0 & \cdots & -pu_{n-1} & -(1/\Delta t)-pm_{n-1} \end{array} \right
%
\begin{bmatrix}
B_{i-1,1} \\
B_{i-1,2} \\
\vdots \\
B_{i-1,n-1}
\end{bmatrix} 
\\
=
\left( \begin{array}{cccccc}
-(1/\Delta t)+pm_{1} & pd_{1} & 0 & \cdots  & 0 & 0\\
pu_{2} & -(1/\Delta t)+pm_{2} & pd_{2} &\cdots & 0 & 0 \\
& pu_{3} & 1+b_{3} & \cdots & 0 & 0  \\
& \vdots &\vdots & \ddots & \vdots & \vdots \\ 
& 0 & 0 & \cdots & -pu_{n-1} & -(1/\Delta t+pm_{n-1} \end{array} \right) 
%
\begin{bmatrix}
B_{i,1} \\
B_{i,2} \\
\vdots \\
B_{i,n-1}
\end{bmatrix}
+
\begin{bmatrix}
pu_{1}B_{i-1,0} \\
0 \\
\vdots \\
0 \\
pd_{j-1}B_{i-1,n-1}
\end{bmatrix}
+
 \begin{bmatrix}
pu_{1}B_{i,0} \\
0 \\
\vdots \\
0 \\
pd_{j-1}B_{i,n-1}
\end{bmatrix}  
$$

>>>>

$$B_{i-1,j}=p_u(j)B_{i,j-1}+p_m(j)B_{i,j}+p_d(j)B_{i,j+1}$$

@@

Note that:       
$$p_u(j)=(r_j/\Delta t)^{-1}(\frac{\sigma^{2}}{2(\Delta r_j)^{2}}+\frac{\alpha-\beta r_j}{2\Delta r_j})$$
$$p_m(j)=(r_j/\Delta t)^{-1}(\frac{1}{\Delta t}-\frac{\sigma^2}{\Delta r_j}^{2})$$
$$p_d(j)=(r_j/\Delta t)^{-1}(\frac{\sigma^{2}}{2(\Delta r_j)^{2}}+\frac{\alpha-\beta r_j}{2\Delta r_j})$$

@@

$$\begin{bmatrix}
	B_{i-1,1} \\
	B_{i-1,2} \\
	\vdots \\       
	B_{i-1,n-1}
	\end{bmatrix}
=
\left( \begin{array}{cccccc}
p_m(1) & p_d(1) & 0 & \cdots  & 0 & 0\\
p_u(2) & p_m(2) & p_d(2) &\cdots & 0 & 0 \\
& p_u(3) & p_m(3) & \cdots & 0 & 0  \\
& \vdots &\vdots & \ddots & \vdots & \vdots \\ 
& 0 & 0 & \cdots & p_u(n-1) & p_m(n-1) \end{array} \right) 
%
\begin{bmatrix}
	B_{i,1} \\
	B_{i,2} \\
	\vdots \\       
	B_{i,n-1}
\end{bmatrix}
+
 \begin{bmatrix}
	p_u(1)B_{i,0} \\
	0 \\
	\vdots \\
	0 \\
	p_d(j-1)B_{i,n-1}
	\end{bmatrix}  
$$

@@

$$B_{i+1,j}= p_u(j)B_{i,j-1}+p_m(j)B_{i,j}+p_d(j)B{i,j+1} $$

@@

$$p_u(j)= (\frac{\alpha-\beta r_{j+1}}{2\Delta r} - \frac{\sigma^2}{2\Delta r^2})\Delta t$$ 
$$p_m(j)= (r_{j+1}+\frac{1}{\Delta t} + \frac{\sigma^2}{\Delta r ^2})\Delta t$$
$$p_d(j)= (\frac{\alpha-\beta r_{j+1}}{2\Delta r} + \frac{\sigma^2}{2\Delta r^2})(-\Delta t) $$

@@

$$\left( \begin{array}{cccccc}
p_m(1) & p_d(1) & 0 & \cdots  & 0 & 0\\
p_u(2) & p_m(2) & p_d(2) &\cdots & 0 & 0 \\
& p_u(3) & p_m(3) & \cdots & 0 & 0  \\
& \vdots &\vdots & \ddots & \vdots & \vdots \\ 
& 0 & 0 & \cdots & p_d(n-1) & p_m(n-1) \end{array} \right)
%
\begin{bmatrix}
B_{i,1} \\
B_{i,2} \\
\vdots \\
B_{i,n-1}
\end{bmatrix}
=
\begin{bmatrix}
B_{i+1,1} \\
B_{i+1,2} \\
\vdots \\
B_{i+1,r_{n-1}}
\end{bmatrix}
+
\begin{bmatrix}
-p_u(1)B_{i,0} \\
0 \\
\vdots \\
0 \\
-p_d(j-1)B_{i, r_{n-1}}
\end{bmatrix}
$$

@@

$$p_u(j)=\frac{\alpha-\beta r_{j+1}}{4\Delta r} - \frac{\sigma^2}{4\Delta r^2}$$
$$p_m(j)= \frac{\sigma^2}{2 (\Delta r)^2}+\frac{r_{j}}{2}$$
$$p_d(j)=-\frac{\alpha-\beta r_{j+1}}{4\Delta r} - \frac{\sigma^2}{4\Delta r^2}$$

@@

$$AB_{i-1}=CB_{i}+F_{i-1}+F_{i}$$

$$A= \left( \begin{array}{cccccc}
-(1/\Delta t)-p_m(1) & -p_d(1) & 0 & \cdots  & 0 & 0\\
-p_u(2) & -(1/\Delta t)-p_m(2) & -p_d(2) &\cdots & 0 & 0 \\
& -p_u(3) & -(1/\Delta t)-p_m(3) & \cdots & 0 & 0  \\
& \vdots &\vdots & \ddots & \vdots & \vdots \\ 
& 0 & 0 & \cdots & -p_u(n-1) & -(1/\Delta t)-p_m(n-1) \end{array} \right)
$$

$$C=\left( \begin{array}{cccccc}
-(1/\Delta t)+p_m(1) & p_d(1) & 0 & \cdots  & 0 & 0\\
p_u(2) & -(1/\Delta t)+p_m(2) & p_d(2) &\cdots & 0 & 0 \\
& p_u(3) & 1+b_{3} & \cdots & 0 & 0  \\
& \vdots &\vdots & \ddots & \vdots & \vdots \\ 
& 0 & 0 & \cdots & -p_u(n-1) & -(1/\Delta t+p_m(n-1) \end{array} \right) 
$$
